Contribution Title\thanks{Supported by organization x.}

### 2019-12-09 sections/i_uip.tex
i-uip pure clause can be minimized, add a step of minimization in the algo

\section{Find i-uip Clause}
Classical CDCL SAT solvers analyze each conflict with 1-UIP resolution learning scheme to derive an asserting clause $\oneUIPClause$. Even though prior studies shows that further resolutions on $\oneUIPClause$ against the assertion trail $\assertionTrail$ cannot reduce the clause's literal block distance ($\LBD$), the resolutions could potentially reduce the clause's size. Clause size is an important quality measurement because a smaller clause 1) consumes less memory, 2) requires less steps to force a literal and 3) decreases the size of future conflict clauses.

@@

\begin{algorithm}[t]
\caption{\IUIP}\label{alg:i-uip}
\begin{algorithmic}[1]
\Require  $\oneUIPClause$ is a valid and minimized 1-UIP clause
\Require  $\assertionTrail$ is a valid assertion trail
\Procedure{\IUIP}{$\oneUIPClause, \assertionTrail$} 
    \State $\iUIPClause \gets \oneUIPClause $ \Comment{initialize i-UIP clause} \label{ln:init}
    \State \code{DecisionLvs} $\gets$ Decision levels in $\oneUIPClause$ in descending order
\For{$i \in \code{DecisionLvs}$} \label{ln:iterDecisionLvls}
    \State $L_{i} \gets \Set{l}{\code{level}(l) = i \wedge l \in \iUIPClause}$
    \While{$|\code{unmarked}(L_i)| > 1$} \label{ln:uip}
        \State $p \gets \text{lit with the highest trail position in } L_{i} $ \label{ln:trailaccess}
        \If{$\exists q \in \code{Reason}(\neg{p}, \assertionTrail) \cdot \code{level}(q) \not\in$ \code{DecisionLvs}} \label{ln:resolvable}
            \If{$\IUIPPURE$}
                \State Unresolve literals at level $i$  \label{ln:unresolve}
                \State Go to the next decision level $i$ \label{ln:abondon}
            \ElsIf{$\IUIPMIN$}
                \State $\code{Mark}(p)$ \label{ln:mark}
            \EndIf
        \Else 
            \State  $\iUIPClause \gets (\oneUIPClause ) \bowtie \code{Reason}(\neg{p}, \assertionTrail)$
           \State  $\code{Update}(L_{i})$
        \EndIf
    \EndWhile
\EndFor \label{ln:endCompleteResolution}
\If{$|\iUIPClause| < |\oneUIPClause|$} \label{ln:checkSize}
    \State \textbf{return} $\iUIPClause$
\Else
    \State \textbf{return} $\oneUIPClause$
\EndIf  \label{ln:cSizeCheck}
\EndProcedure
\end{algorithmic}
\end{algorithm}

The algorithm $\IUIP$ computes $\iUIPClause$ from (line~\ref{ln:init} to \ref{ln:endCompleteResolution}), and then returns the smaller clause between 
$\oneUIPClause$ and $\iUIPClause$ (line~\ref{ln:checkSize} to \ref{ln:cSizeCheck}). 
The algorithm first initializes $\iUIPClause$ with the minimized\cite{} $\oneUIPClause$. Next, the algorithm iterate through the decision levels of $\iUIPClause$ in descending order (line~\ref{ln:iterDecisionLvls}) and tries to find the unique implication point in each level (line~\ref{ln:uip}). Since $\IUIP$ needs to preserve $\iUIPClause$'s $\LBD$ during resolutions, before resolving away a target literal $p$, the algorithm preemptively checks whether the reasoning clause of $\neg{p}$ contains any literal $q$ from an unseen decision level (line~\ref{ln:resolvable}). If such a literal $q$ exists, then the algorithm cannot find the unique implication point (UIP) at the current level $i$ because resolving away $p$ will introduce $q$ into the clause and increases $\LBD$. One solution is to abandon level $i$ by reverting back to the state before any literal at level $i$ is resolved away (line~\ref{ln:unresolve}), and then move on to the next level (line~\ref{ln:abondon}). We denote $\IUIP$ learning with this solution as $\IUIPPURE$. The final $\iUIPClause$ produced by $\IUIPPURE$ will contains exactly one literal for levels where the LBD-persevering UIP exist. However, $\IUIPPURE$ does not minimize the number of literals in the decision levels where the LBD-preserving UIP does not exist.

  When $\IUIP$ cannot resolve away a literal $p$ without increasing $\iUIPClause$'s LBD, instead of skipping the entire decision level $i$, a more practical solution $\IUIPMIN$ will mark and keep $p$ in $\iUIPClause$ (line~\ref{ln:mark}), and continue resolutions at level $i$. $\IUIPMIN$ will ignore all the unsolvable literals and find the "local" unique implication point at every decision level.  The algorithm terminates when there is exactly one unmarked literal left for each decision level of $\iUIPClause$, representing the local unique implication points.

>>>>

\section{Find i-uip Clause} \label{sec:i-uip}
Classical CDCL SAT solvers analyze each conflict with 1-UIP resolution learning scheme to derive an asserting clause $\oneUIPClause$. Even though prior studies shows that further resolutions on $\oneUIPClause$ against the assertion trail $\assertionTrail$ cannot reduce the clause's literal block distance ($\LBD$), the resolutions could potentially reduce the clause's size. Clause size is an important quality measurement because a smaller clause 1) consumes less memory, 2) requires less steps to force a literal and 3) decreases the size of future conflict clauses.

@@

\begin{algorithm}[t]
\caption{\IUIP}\label{alg:i-uip}
\begin{algorithmic}[1]
\Require  $\oneUIPClause$ is a valid and minimized 1-UIP clause
\Require  $\assertionTrail$ is a valid assertion trail
\Procedure{\IUIP}{$\oneUIPClause, \assertionTrail$} 
    \State $\iUIPClause \gets \oneUIPClause $ \Comment{initialize i-UIP clause} \label{ln:init}
    \State \code{DecisionLvs} $\gets$ Decision levels in $\oneUIPClause$ in descending order
\For{$i \in \code{DecisionLvs}$} \label{ln:iterDecisionLvls}
    \State $L_{i} \gets \Set{l}{\code{level}(l) = i \wedge l \in \iUIPClause}$
    \While{$|\code{unmarked}(L_i)| > 1$} \label{ln:uip}
        \State $p \gets \text{lit with the highest trail position in } L_{i} $ \label{ln:trailaccess}
        \If{$\exists q \in \code{Reason}(\neg{p}, \assertionTrail) \cdot \code{level}(q) \not\in$ \code{DecisionLvs}} \label{ln:resolvable}
            \If{$\IUIPPURE$}
                \State Unresolve literals at level $i$  \label{ln:unresolve}
                \State Go to the next decision level $i$ \label{ln:abondon}
            \ElsIf{$\IUIPMIN$}
                \State $\code{Mark}(p)$ \label{ln:mark}
            \EndIf
        \Else 
            \State  $\iUIPClause \gets (\oneUIPClause ) \bowtie \code{Reason}(\neg{p}, \assertionTrail)$
           \State  $\code{Update}(L_{i})$
        \EndIf
    \EndWhile
\EndFor \label{ln:endCompleteResolution}
\\
\If{$\IUIPPURE$}\label{ln: 2ndMinStart}   \Comment{$\iUIPClause$ from $\IUIPPURE$ can be minimized}
    \State $\iUIPClause  \gets \textbf{Minimize}(\iUIPClause)$ 
\EndIf\label{ln: 2ndMinEnd}
\\
\If{$|\iUIPClause| < |\oneUIPClause|$} \label{ln:checkSize}
    \State \textbf{return} $\iUIPClause$
\Else
    \State \textbf{return} $\oneUIPClause$
\EndIf  \label{ln:cSizeCheck}
\EndProcedure
\end{algorithmic}
\end{algorithm}

The algorithm $\IUIP$ computes $\iUIPClause$ from (line~\ref{ln:init} to \ref{ln:endCompleteResolution}), and then returns the smaller clause between 
$\oneUIPClause$ and $\iUIPClause$ (line~\ref{ln:checkSize} to \ref{ln:cSizeCheck}). 
The algorithm first initializes $\iUIPClause$ with the minimized\cite{} $\oneUIPClause$. Next, the algorithm iterate through the decision levels of $\iUIPClause$ in descending order (line~\ref{ln:iterDecisionLvls}) and tries to find the unique implication point in each level (line~\ref{ln:uip}). Since $\IUIP$ needs to preserve $\iUIPClause$'s $\LBD$ during resolutions, before resolving away a target literal $p$, the algorithm preemptively checks whether the reasoning clause of $\neg{p}$ contains any literal $q$ from an unseen decision level (line~\ref{ln:resolvable}). If such a literal $q$ exists, then the algorithm cannot find the unique implication point (UIP) at the current level $i$ because resolving away $p$ will introduce $q$ into the clause and increases $\LBD$. One solution is to abandon level $i$ by reverting back to the state before any literal at level $i$ is resolved away (line~\ref{ln:unresolve}), and then move on to the next level (line~\ref{ln:abondon}). We denote $\IUIP$ learning with this solution as $\IUIPPURE$. The final $\iUIPClause$ produced by $\IUIPPURE$ will contains exactly one literal for levels where the LBD-persevering UIP exist. However, $\IUIPPURE$ does not minimize the number of literals in the decision levels where the LBD-preserving UIP does not exist, and clause minimization techniques\cite{} can be used to further reduce the clause size (line~\ref{ln: 2ndMinStart} to \ref{ln: 2ndMinEnd}).

  When $\IUIP$ cannot resolve away a literal $p$ without increasing $\iUIPClause$'s LBD, instead of skipping the entire decision level $i$, a more practical solution $\IUIPMIN$ will mark and keep $p$ in $\iUIPClause$ (line~\ref{ln:mark}), and continue the resolutions at level $i$. $\IUIPMIN$ will ignore all the unsolvable literals and find the "local" unique implication point at every decision level.  The algorithm terminates when there is exactly one unmarked literal left for each decision level of $\iUIPClause$, representing the local unique implication points. The clause $\iUIPClause$ learnt by
  $\IUIPMIN$ is minimized\footnote{clause size cannot be reduced via minimization techniques\cite{}.}, we defer the minimization proof to Appendix~\ref{}.
